---
title: "Travis CI Test"
author: "Alex Axthelm"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    theme: readable
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, message=FALSE}
library(ggplot2)
library(DT)
library(plotly)
library(PKI)
library(secure)
```



# Introduction
This page is intended to provide a test to my ability to render RMarkdown documents and deploy to GithubPages using TravisCI

## Show some R code
```{r}
1 + 1
5:10
```

```{r}
head(mtcars)
```

Show me a plot
```{r}
carplot <- ggplot(data = mtcars, aes(
  x = wt,
  y = mpg,
  color = factor(vs)
)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(. ~ am)
```

```{r}
carplot
```

## htmlwidgets
### Plotly
```{r}
ggplotly(carplot)
```

### datatable
```{r}
datatable(
  mtcars,
  extensions = c("Buttons",
                 "FixedColumns"#,
                 # "Responsive"
                 ),
  options = list(
    dom = "Bfrtip",
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
    scrollX = TRUE,
    fixedColumns = list(leftColumns = 1)
  )
)
```

## Secure
Let's try using Hadley's `Secure` package

```{r initialize_secure}
# secure::add_user("Alex Axthelm", local_key())
# secure::add_user("AlexAxthelm_gh", github_key("AlexAxthelm"))
# secure::add_user("travis", travis_key("AlexAxthelm/travis_render_test"))
```

This should show the results of secret data frame that was encrypted on a development machine, and rendered here on Travis.
```{r Load_secret_data}
# the secret data frame is iris.
Sys.getenv("OS")
Sys.getenv("CONTINUOUS_INTEGRATION")

local_key()

# Note that secure returns a list, so we need to do a list operator to get the actual data.
secret_data <- decrypt("this_is_iris")[[1]]
identical(secret_data, iris)
```

```{r}
enc_df <- mtcars %>% filter(am ==1)
secure::encrypt("enc_df", key = "abcdasdf", secret = enc_df)
head(enc_df)
remove(enc_df)
try(head(enc_df))
```

```{r}
secure::decrypt("enc_df")
```
